\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2018-10-12 paper/main.tex
finished pass through supplemental figures document
corrected kurtosis thresholding description, addressed ACH letter comments

We first applied fourth order Butterworth notch filter to remove 60 Hz
($\pm$ .5 Hz) line noise from every recording (from every electrode).
Next, we downsampled the recordings (regardless of the original
samplerate) to 250 Hz.  (This downsampling step served to both
normalize for differences in sampling rates across patients and to
ease the computational burden of our subsequent analyses.)  We then
excluded any electrodes that showed putative epileptiform activity.
Specifically, we excluded from further analysis any electrode that
exhibited an average kurtosis of 10 or greater across all of that
patient's recording sessions.  We also excluded any patients with
fewer than 2 electrodes that passed this criteria, as the SuperEEG
algorithm requires measuring correlations between 2 or more electrodes
from each patient.  For Dataset 1, this yielded clean recordings from
4168 electrodes implanted throughout the brains of 67 patients
(Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
recordings from 3159 electrodes from 24 patients.  Each individual
patient contributes electrodes from a limited set of brain locations,
which we localized in a common space~\citep[MNI152;][]{GrabEtal06}; an
example Dataset 1 patient's 54 electrodes that passed the above
kurtosis threshold test are highlighted in black and red.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information
      score by voxel.}  This panel is in the same format as Panel A.
    In both panels the contours indicate the intersections between
    the top 10\% most informative voxels in each map.
    \textbf{C. Correspondence in information scores by voxel across
      Datasets 1 and 2.}  Same format as Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

>>>>

We first applied fourth order Butterworth notch filter to remove 60 Hz
($\pm$ .5 Hz) line noise from every recording (from every electrode).
Next, we downsampled the recordings (regardless of the original
samplerate) to 250 Hz.  (This downsampling step served to both
normalize for differences in sampling rates across patients and to
ease the computational burden of our subsequent analyses.)  We then
excluded any electrodes that showed putative epileptiform activity.
Specifically, we excluded from further analysis any electrode that
exhibited an maximum kurtosis of 10 or greater across all of that
patient's recording sessions.  We also excluded any patients with
fewer than 2 electrodes that passed this criteria, as the SuperEEG
algorithm requires measuring correlations between 2 or more electrodes
from each patient.  For Dataset 1, this yielded clean recordings from
4168 electrodes implanted throughout the brains of 67 patients
(Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
recordings from 3159 electrodes from 24 patients.  Each individual
patient contributes electrodes from a limited set of brain locations,
which we localized in a common space~\citep[MNI152;][]{GrabEtal06}; an
example Dataset 1 patient's 54 electrodes that passed the above
kurtosis threshold test are highlighted in black and red.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information
      score by voxel.}  This panel is in the same format as Panel A.
    In both panels the contours indicate the intersections between the
    top 10\% most informative voxels in each map (also see
    Fig.~\intersectmap).  \textbf{C. Correspondence in information
      scores by voxel across Datasets 1 and 2.}  Same format as
    Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

### 2018-10-12 paper/supporting_information.tex
corrected kurtosis thresholding description, addressed ACH letter comments

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_4}
\caption{\textbf{Reconstruction accuracy versus within-subject data
    features for two ECoG datasets.} \textbf{A.--F.  Features from
    Dataset 1.}  Features include: (\textbf{A.}) total number of
  electrodes implanted in each patient's brain, (\textbf{B.})
  per-patient number of electrodes that were filtered out due to
  having an average kurtosis greater than 10, (\textbf{C.})
  per-patient proportion of electrodes that were filtered out due to
  having an average kurtosis greater than 10, (\textbf{D.})
  per-patient number of recording sessions, (\textbf{E.}) per-patient
  total recording time (h), and (\textbf{F.}) per-patient average
  session length (h).  \textbf{G.--L. Features from Dataset 2.}
  Analogous format to Panels A--F.}
\label{fig:supplemental_4}
\end{figure}

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_4}
\caption{\textbf{Reconstruction accuracy versus within-subject data
    features for two ECoG datasets.} \textbf{A.--F.  Features from
    Dataset 1.}  Features include: (\textbf{A.}) total number of
  electrodes implanted in each patient's brain, (\textbf{B.})
  per-patient number of electrodes that were filtered out due to
  having an maximum kurtosis greater than 10 across all recording
  sessions, (\textbf{C.})  per-patient proportion of electrodes that
  were filtered out due to having an average kurtosis greater than 10,
  (\textbf{D.})  per-patient number of recording sessions,
  (\textbf{E.}) per-patient total recording time (h), and
  (\textbf{F.}) per-patient average session length (h).
  \textbf{G.--L. Features from Dataset 2.}  Analogous format to Panels
  A--F.}
\label{fig:supplemental_4}
\end{figure}
